\chapter*{Work Plan}
\addcontentsline{toc}{chapter}{Work Plan}

\begin{itemize}
    \item \textbf{Year 1:} \textbf{Foundational Work and Framework Setup} 
        \begin{itemize}
            \item Dataset collection from DrugBank, TG-GATEs, FAERS, TCGA, ClinicalTrials.gov.
            \item Preprocessing Pipelines for omics and drug data.
            \item Build a baseline PK/PD mechanistic models.
            \item Publication target for Review and AI on Digital Twins.
        \end{itemize}
    \item \textbf{Year 2:} \textbf{Model Development and Organ-Specific Twins}
        \begin{itemize}
            \item Implement GNN for drug-target-organ prediction.
            \item Develop liver and kidney digital twins using TG-GATEs and FAERS data'
            \item Begin toxicity prediction pipelines.
            \item Initial validation against retrospective trial data.
            \item Publication target for GNN-powered Digital Twins.
        \end{itemize}
    \item \textbf{Year 3:} \textbf{Reinforcement Learning and Personalization}
        \begin{itemize}
            \item Implement Reinforcement Learning for Dose Optimization.
            \item Integrate multi-omics data for (TCGA, LINCS) for patient specific twins.
            \item Build explainability modules (SHAP, LIME)
            \item Large scale simulateions for oncology and metabolic diseases.
            \item Publication target for RL dose optimization paper and multi-omics personalization paper.
        \end{itemize}
    \item \textbf{Year 4:} \textbf{Validation, Translation, and Dissemination}
        \begin{itemize}
            \item Retrospective validation using CinicalTrials.gov oncology datasets.
            \item Industry collaboration for regulatory alignment.
            \item Economic alignment of trial cost/time reduction.
            \item Publication target for Regulatory pathways paper and Economic impact study.
        \end{itemize}
\end{itemize}