\chapter*{Expected Outcomes}
\addcontentsline{toc}{chapter}{Expected Outcomes}

This project will deliver both scientific and practical tools for AI-driven drug discovery.
\begin{itemize}
    \item \textbf{Novel AI Framework:} A validated multi-organ digital twin platform capable of simulating drug efficacy, toxicity and optimal dosing insilico.
    \item \textbf{Publications:} At least 8 high-impact publications including methodology, papers, validation studies, and regulatory alignment articles.
    \item \textbf{Datasets and Pipelines:} Curated and Preprocessed datasets (DrugBank, TG-GATEs, FAERS, TCGA) AND Reproducible pipelines made available under FAIR principles.
    \item \textbf{AI Models:} 
        \begin{itemize}
            \item \textbf{GNN Model:} For drug-organ interaction.
            \item \textbf{Reinforcement Learning} For adaptive dosing
            \item \textbf{Explainable AI:} To enhance trust and regulatory acceptance.
        \end{itemize}
    \item \textbf{Regulatory Insights:} Framework for aligning digital twin outputs with FDA standards, supporting early regulatory adoption of in silico trials.
    \item \textbf{Economic Evaluation:} Quantitative assessment showing potential reductions in trial cost and duration, positioning digital twins as cost-effective complements to Phase I/II trials.
    \item \textbf{Industry Relevance:} Prototype collaboration-ready Software package facilitate translation  into pharma ready pipelines.     
\end{itemize}

Ultimately, this project will demonstrate that AI-powered digital twins can reduce trial failure rates, accelarate therapy development, and support precision medicine initiatives, bridging academic innovation with
industry and regulatory needs. 